Fusing Filters with Integer Linear Programming

### 2014-05-15 2014betterfusionforfilters/section/05-Benchmarks.tex
benchmark

%!TEX root = ../Main.tex
\section{Benchmarks}
\label{s:Benchmarks}
\ben{Use the larger programs as benchmarks, or as running examples. We only need small, simple programs to demonstrate how the algorithm works.}

@@

Notes:
\begin{itemize}
% \item
% Normalize2 tested with around 1gb input data. This should be small enough that all intermediates fit in memory, but large enough not to fit in cache.
% \item
% ClosestPoints only tested with 80mb data.
\item
In some cases, the clusterings generated by the different methods were the same. In this case, the results are also the same. 
\item
The stream fusion benchmarks use the clustering that stream fusion \emph{would} use, but hand-fused and written in C.
\item
Programs were run five times with the same input data, and the fastest run was used.
\item
ILP solutions were created by hand-fusing based on the clustering of the implementation. In the future, this will be integrated to use data flow fusion.
\item
Benchmark programs are available at \url{https://github.com/amosr/papers/tree/master/2014betterfusionforfilters/benches}
\end{itemize}

\subsection{Example}
The normalize2 example is already in combinator normal form.
\begin{code}
 normalize2 :: Array Int -> Array Int
 normalize2 xs
  = let sum1 = fold   (+)  0   xs
        gts  = filter (> 0)    xs
        sum2 = fold   (+)  0   gts
        ys1  = map    (/ sum1) xs
        ys2  = map    (/ sum2) xs
    in (ys1, ys2)
\end{code}

>>>>

%!TEX root = ../Main.tex
\section{Benchmarks}
\label{s:Benchmarks}

@@

We have run three benchmarks to constrast our clustering algorithm, Megiddo~\cite{megiddo1998optimal}'s clustering, and the clustering produced by stream fusion\cite{coutts2007streamfusion}.
The three benchmarks are the @normalize2@ example, finding the closest pair of points, and quadtree.
The benchmark programs are all hand-written, hand-fused C code based on the clustering.
Each program was ran with the same input five times, and the minimum runtime was used.

Benchmark programs are available at \url{https://github.com/amosr/papers/tree/master/2014betterfusionforfilters/benches}

\subsection{Normalize2}
The normalize2 example is already in combinator normal form.
\begin{code}
 normalize2 :: Array Int -> Array Int
 normalize2 xs
  = let sum1 = fold   (+)  0   xs
        gts  = filter (> 0)    xs
        sum2 = fold   (+)  0   gts
        ys1  = map    (/ sum1) xs
        ys2  = map    (/ sum2) xs
    in (ys1, ys2)
\end{code}
